\Large{Holier Than Thou? No Partisan Gap in the Consumption\\ of Pornography Online}\footnote{You can download the replication materials from \href{http://github.com/soodoku/adult}{https://github.com/soodoku/adult}}

### 2023-01-04 ms/adult.tex
revise ms

The consumption of pornography is also highly concentrated among a few sites, with ten most frequented pornography sites receiving more than 12 times the traffic to all other porn sites  (approximately 109 minutes vs. 9 minutes, see \cref{fig:concentration_porn_consumption}). Close to 80 percent of the traffic to pornographic sites is to just one pornographic site. Looking at the characteristics of consumers of pornography, expectedly, consumers of pornography online are younger and are more likely to be male \cref{fig:} %TODO

@@

Given the skew in the data, we ran a quantile regression, regressing the duration on party. As Figures \ref{fig:quantile_regression_duration} and \ref{fig:quantile_regression_prop_duration} show, there are no significant differences in consumption of pornographic content between the parties. To account for the possibility that this may be a result of confounding demographic differences between the parties, we control for immutable characteristics like age and gender. (\cref{tab:characteristics_split_by_party} shows differences in age, gender, and race by party identification.) We use these variables in our analyses of pornography consumption below. Given how concentrated pornographic consumption is in our data, it is unlikely to make much of a difference and that is indeed what we find --- see Figure \ref{fig:quantile_regression_duration}. 
%===========================
% Quantile regressions
% Hours spent on adult sites
%===========================
\begin{figure}[t]
	\centering
	\caption{Quantile Estimates--Hours Spent on Porn Sites by Party}
	\includegraphics[width=.7\linewidth]{../figs/quantile_reg_duration_adult.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Dependent variable is the number of hours individuals in our sample spent on porn sites.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
		95\% confidence intervals constructed from standard errors.
		See \cref{fig:quantile_regression_duration_covariates} for the same plot controlling for individual characteristics.
	}
	\label{fig:quantile_regression_duration}
\end{figure}

%========================================
% Quantile regressions
% Proportion of time spent on adult sites
%========================================
\begin{figure}[t]
	\centering
	\caption{Quantile Estimates--Percentage of Time Spent on Porn Sites by Party}
	\includegraphics[width=.7\linewidth]{../figs/quantile_reg_proportion_duration_adult.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Dependent variable is the percentage of time individuals in our sample spent on porn sites.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
		95\% confidence intervals constructed from standard errors.
		See \cref{fig:quantile_regression_prop_duration_covariates} for the same plot controlling for individual characteristics.
	}
	\label{fig:quantile_regression_prop_duration}
\end{figure}

@@

\subsection{Skew in Website Visits}
%============================
% Figure of top 25 adultsites
%============================
\begin{figure}[ht]
	\centering
	\caption{Top 25 Porn Sites}
	\includegraphics[width=\textwidth]{../figs/top_25_adultsites.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Table shows the top 25 porn sites that individuals visit in the sample period.
		Pornography sites are as categorized by YouGov (see the \nameref{sec:data} section).
		The \emph{Hours} column are the total number of hours that individuals in the sample spent on the site. 
		The \emph{Visits} column is total number of visits by individuals in the sample to the site.  
		Sites to the right of the vertical dashed are the top 1 percent of porn sites.
	}
	\label{fig:top25_adult}
\end{figure}

%================================
% Figure of top 25 non-adultsites
%================================
\begin{figure}
	\centering
	\caption{Top 25 (Non-Porn) Domains}
	\includegraphics[width=\textwidth]{../figs/top_25_nonadultsites.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Table shows the top 25 non-pornographic sites that individuals visit in the sample period.
		The \emph{Hours} column are the total number of hours that individuals in the sample spent on the site. 
		The \emph{Visits} column is total number of visits by individuals in the sample to the site.  			
		Sites to the right of the vertical dashed are the top 1 percent (of non-porn sites).
	}
	\label{fig:top25_nonadult}
\end{figure}

@@

%====================================
% Figure of traffic to top x websites
%====================================
\begin{figure}
	\centering
	\caption{Traffic to Top x Porn Sites by Party}
	\includegraphics[width=.6\textwidth]{../figs/concentration_porn_consumption_topX_by_party.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Figure shows concentration of porn consumption based on individuals' most frequented porn sites.
		Shaded areas are 95\% confidence intervals from bootstrapped standard errors (n = 1,000).
	}
	\label{fig:concentration_porn_consumption_topX_by_party}
\end{figure}

>>>>

The consumption of pornography is also highly concentrated among a few sites, with ten most frequented pornography sites receiving more than 12 times the traffic to all other pornographic sites  (approximately 109 minutes vs. 9 minutes, see \cref{fig:concentration_porn_consumption}). Close to 80 percent of the traffic to pornographic sites is to just one pornographic site. Looking at the characteristics of consumers of pornography, expectedly, consumers of pornography online are younger and are more likely to be male \cref{fig:} %TODO

@@

Given the skew in the data, we ran a quantile regression, regressing the duration on party. As Figures \ref{fig:quantile_regression_duration} and \ref{fig:quantile_regression_prop_duration} show, there are no significant differences in consumption of pornographic content between the parties. To account for the possibility that this may be a result of confounding demographic differences between the parties, we control for immutable characteristics like age and gender. (\cref{tab:characteristics_split_by_party} shows differences in age, gender, and race by party identification.) We use these variables in our analyses of pornography consumption below. Given how concentrated pornographic consumption is in our data, it is unlikely to make much of a difference and that is indeed what we find --- see Figure \ref{fig:quantile_regression_duration}. 
%===========================
% Quantile regressions
% Hours spent on adult sites
%===========================
\begin{figure}[t]
	\centering
	\caption{Quantile Estimates--Hours Spent on Pornographic Sites by Party}
	\includegraphics[width=.7\linewidth]{../figs/quantile_reg_duration_adult.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Dependent variable is the number of hours individuals in our sample spent on pornographic sites.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
		95\% confidence intervals constructed from standard errors.
		See \cref{fig:quantile_regression_duration_covariates} for the same plot controlling for individual characteristics.
	}
	\label{fig:quantile_regression_duration}
\end{figure}

%========================================
% Quantile regressions
% Proportion of time spent on adult sites
%========================================
\begin{figure}[t]
	\centering
	\caption{Quantile Estimates--Percentage of Time Spent on Pornographic Sites by Party}
	\includegraphics[width=.7\linewidth]{../figs/quantile_reg_proportion_duration_adult.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Dependent variable is the percentage of time individuals in our sample spent on pornographic sites.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
		95\% confidence intervals constructed from standard errors.
		See \cref{fig:quantile_regression_prop_duration_covariates} for the same plot controlling for individual characteristics.
	}
	\label{fig:quantile_regression_prop_duration}
\end{figure}

@@

\subsection{Skew in Website Visits}
%============================
% Figure of top 25 adultsites
%============================
\begin{figure}[ht]
	\centering
	\caption{Top 25 Pornography Sites}
	\includegraphics[width=\textwidth]{../figs/top_25_adultsites.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Table shows the top 25 pornographic sites that individuals visit in the sample period.
		Pornography sites are as categorized by YouGov (see the \nameref{sec:data} section).
		The \emph{Hours} column are the total number of hours that individuals in the sample spent on the site. 
		The \emph{Visits} column is total number of visits by individuals in the sample to the site.  
		Sites to the right of the vertical dashed are the top 1 percent of pornographic sites.
	}
	\label{fig:top25_adult}
\end{figure}

%================================
% Figure of top 25 non-adultsites
%================================
\begin{figure}
	\centering
	\caption{Top 25 (Non-Porn) Domains}
	\includegraphics[width=\textwidth]{../figs/top_25_nonadultsites.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Table shows the top 25 non-pornographic sites that individuals visit in the sample period.
		The \emph{Hours} column are the total number of hours that individuals in the sample spent on the site. 
		The \emph{Visits} column is total number of visits by individuals in the sample to the site.  			
		Sites to the right of the vertical dashed are the top 1 percent (of non-pornographic sites).
	}
	\label{fig:top25_nonadult}
\end{figure}

@@

%====================================
% Figure of traffic to top x websites
%====================================
\begin{figure}
	\centering
	\caption{Traffic to Top x Pornographic Sites by Party}
	\includegraphics[width=.6\textwidth]{../figs/concentration_porn_consumption_topX_by_party.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Figure shows concentration of pornography consumption based on individuals' most frequented pornographic sites.
		Shaded areas are 95\% confidence intervals from bootstrapped standard errors (n = 1,000).
	}
	\label{fig:concentration_porn_consumption_topX_by_party}
\end{figure}
